Multi-modality Imagery Database for Plant Phenotyping

### 2015-05-02 datapaper_baseline.tex
baseline

\begin{figure*}
\begin{centering}
\begin{tabular}{c c@{} c@{} c@{} c@{} c@{} c@{} c@{} c@{} c@{}}
%\begin{tabular}{lllllllll}
(a) &
\includegraphics[trim= 10 100 20 100, clip, width=.1\textwidth]{Figures/trackExample/1_1}&
\includegraphics[trim= 50 150 100 200, clip, width=.1\textwidth]{Figures/trackExample/1_2}&
\includegraphics[trim= 50 150 100 200, clip, width=.1\textwidth]{Figures/trackExample/1_3}&
\includegraphics[trim= 50 150 100 200, clip, width=.1\textwidth]{Figures/trackExample/1_4}&
\includegraphics[trim= 50 150 100 200, clip, width=.1\textwidth]{Figures/trackExample/1_5}&
\includegraphics[trim= 50 150 100 200, clip, width=.1\textwidth]{Figures/trackExample/1_6}&
\includegraphics[trim= 50 150 100 200, clip, width=.1\textwidth]{Figures/trackExample/1_7}&
\includegraphics[trim= 50 150 100 200, clip, width=.1\textwidth]{Figures/trackExample/1_8}&
\includegraphics[trim= 0 100 20 100, clip, width=.1\textwidth]{Figures/trackExample/1_9}\\
(b)&
\includegraphics[width=.1\textwidth]{Figures/trackExample/2_1}&
\includegraphics[width=.1\textwidth]{Figures/trackExample/2_2}&
\includegraphics[width=.1\textwidth]{Figures/trackExample/2_3}&
\includegraphics[width=.1\textwidth]{Figures/trackExample/2_4}&
\includegraphics[width=.1\textwidth]{Figures/trackExample/2_5}&
\includegraphics[width=.1\textwidth]{Figures/trackExample/2_6}&
\includegraphics[width=.1\textwidth]{Figures/trackExample/2_7}&
\includegraphics[width=.1\textwidth]{Figures/trackExample/2_8}&
\includegraphics[width=.1\textwidth]{Figures/trackExample/2_9}\\
(c) &
\includegraphics[width=.1\textwidth]{Figures/trackExample/3_9}&
\includegraphics[width=.1\textwidth]{Figures/trackExample/3_9}&
\includegraphics[width=.1\textwidth]{Figures/trackExample/3_9}&
\includegraphics[width=.1\textwidth]{Figures/trackExample/3_9}&
\includegraphics[width=.1\textwidth]{Figures/trackExample/3_9}&
\includegraphics[width=.1\textwidth]{Figures/trackExample/3_9}&
\includegraphics[width=.1\textwidth]{Figures/trackExample/3_9}&
\includegraphics[width=.1\textwidth]{Figures/trackExample/3_9}&
\includegraphics[width=.1\textwidth]{Figures/trackExample/3_9}\\

>>>>

\begin{figure*}
\begin{centering}
\begin{tabular}{c c@{} c@{} c@{} c@{} c@{} c@{} c@{} c@{} c@{}}
%\begin{tabular}{lllllllll}
(a) &
\includegraphics[trim= 100 100 150 10, clip, width=.1\textwidth]{Figures/trackExample/1_1}&
\includegraphics[trim= 100 100 150 10, clip, width=.1\textwidth]{Figures/trackExample/1_2}&
\includegraphics[trim= 100 100 150 10, clip, width=.1\textwidth]{Figures/trackExample/1_3}&
\includegraphics[trim= 100 100 150 10, clip, width=.1\textwidth]{Figures/trackExample/1_4}&
\includegraphics[trim= 100 100 150 10, clip, width=.1\textwidth]{Figures/trackExample/1_5}&
\includegraphics[trim= 100 100 150 10, clip, width=.1\textwidth]{Figures/trackExample/1_6}&
\includegraphics[trim= 100 100 150 10, clip, width=.1\textwidth]{Figures/trackExample/1_7}&
\includegraphics[trim= 100 100 150 10, clip, width=.1\textwidth]{Figures/trackExample/1_8}&
\includegraphics[trim= 100 100 150 10, clip, width=.1\textwidth]{Figures/trackExample/1_9}\\
(b)&
\includegraphics[trim= 100 100 150 10, clip, width=.1\textwidth]{Figures/trackExample/2_1}&
\includegraphics[trim= 100 100 150 10, clip, width=.1\textwidth]{Figures/trackExample/2_2}&
\includegraphics[trim= 100 100 150 10, clip, width=.1\textwidth]{Figures/trackExample/2_3}&
\includegraphics[trim= 100 100 150 10, clip, width=.1\textwidth]{Figures/trackExample/2_4}&
\includegraphics[trim= 100 100 150 10, clip, width=.1\textwidth]{Figures/trackExample/2_5}&
\includegraphics[trim= 100 100 150 10, clip, width=.1\textwidth]{Figures/trackExample/2_6}&
\includegraphics[trim= 100 100 150 10, clip, width=.1\textwidth]{Figures/trackExample/2_7}&
\includegraphics[trim= 100 100 150 10, clip, width=.1\textwidth]{Figures/trackExample/2_8}&
\includegraphics[trim= 100 100 150 10, clip, width=.1\textwidth]{Figures/trackExample/2_9}\\
(c) &
\includegraphics[trim= 110 100 170 10, clip, width=.1\textwidth]{Figures/trackExample/3_1.pdf}&
\includegraphics[trim= 110 100 170 10, clip, width=.1\textwidth]{Figures/trackExample/3_2.pdf}&
\includegraphics[trim= 110 100 170 10, clip, width=.1\textwidth]{Figures/trackExample/3_3.pdf}&
\includegraphics[trim= 110 100 170 10, clip, width=.1\textwidth]{Figures/trackExample/3_4.pdf}&
\includegraphics[trim= 110 100 170 10, clip, width=.1\textwidth]{Figures/trackExample/3_5.pdf}&
\includegraphics[trim= 110 100 170 10, clip, width=.1\textwidth]{Figures/trackExample/3_6.pdf}&
\includegraphics[trim= 110 100 170 10, clip, width=.1\textwidth]{Figures/trackExample/3_7.pdf}&
\includegraphics[trim= 110 100 170 10, clip, width=.1\textwidth]{Figures/trackExample/3_8.pdf}&
\includegraphics[trim= 110 100 170 10, clip, width=.1\textwidth]{Figures/trackExample/3_9.pdf}\\
